The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-28 exp-resurgence.tex
Redo modified Bessel thimble projection with correct contour

Setting $u = \cosh(t/n)$ and recalling that
\begin{align*}
\cosh(n\tau) & = T_n(\cosh(\tau)) \\
\sinh(m\tau) & = U_{m-1}(\cosh(\tau)) \sinh(\tau),
\end{align*}
we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\mathcal{C}^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
\begin{align}
\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\mathcal{C}^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\mathcal{C}_j}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\mathcal{C}_j}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
\end{align}
where $\mathcal{C}_j$ is the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, as represented in Figure \ref{fig:bessel_unrolled}. Because $\cosh(t)$ is periodic, the integral has the same value for every choice of $\mathcal{C}_j$ with $j\in\Z$.  
\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.3]{figures/Bessel0_unrolled_lightblue.png}
    \caption{The paths $\mathcal{C}_j$.}
    \label{fig:bessel_unrolled}
\end{figure}

For any $\mu \in \C \smallsetminus \Z$, we have a thimble integral representation of $K_{\mu}$ given by formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\textcolor{DarkCyan}{[Cite Watson too?]}
\begin{equation}\label{int:mod-bessel-gen}
 K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\mathcal{C}_0} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
\end{equation}
\begin{verify}
% \begin{align*}
% \notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
% \notag & = \frac{1}{2i \sin(\mu \pi)} \int_{\mathcal{C}'} \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt 
% \end{align*}
% where $\mathcal{C}'$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ 
Following Watson \textit{A treatment of Bessel function}, 1944, pp. 181 (it is the reference in \cite{dlmf})
\begin{align*}
2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b}\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db
\end{align*}
hence 
\begin{align*}
4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big] \\
& = \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right]\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right]\,da \\
& \textcolor{OrangeRed}{= 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da} \\
& = 2\int_{-\infty}^0 e^{z\cosh(-\pi i+a)} \sinh\big(\mu(a-i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh\big(\mu(i\pi+a)\big)\,da
\end{align*}
\color{OrangeRed}
Stop at the highlighted line! This simplifies to the integral
\[ 2 \int_\gamma e^{z\cosh(t)} \sinh(\mu t)\,dt \]
along the contour $\gamma$ that runs rightward along $i\pi + \R$.

\textcolor{magenta}{The integral on the next line is {\em not} the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, because it skips the segment along $i(-\pi, \pi)$.}
\par
\end{verify}
\textcolor{orange}{The integral converges when $z$ is in the right half-plane.} We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
%
%\begin{center}
%    \begin{tikzpicture}
%        \draw[->] (6,2)--(10,2);
%        \draw[->] (8,0)--(8,4);
%        \draw[red,thick,->] (10,1.8) .. controls (8,2) .. (10,2.2);
%        %\draw[red,thick,->] (10,2)--(9,2);
%        %\draw[red,thick] (9,2)--(8.5,2);
%        %\draw[red,thick] (10,2)--(9.3,2);
%        %\draw[red,thick,->] (8.5,2)--(9.3,2);
%        \node[red,below, font=\tiny] at (10,1.8) {$\gamma_z$};
%        \node[font=\tiny,below] at (8.5,2) {$1$};
%    \end{tikzpicture}
%\end{center}

We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of the asymptotic of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
\begin{align*}
    K_\mu(z)& = -\frac{1}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\,\frac{\sinh(\mu t)}{\sinh(t)}\,d\zeta  & \\
    &=-\frac{\mu}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right)\,d\zeta & \cite[15.4.16]{dlmf}
\end{align*}
where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$. Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf} \textcolor{PaleVioletRed}{[Please clean up operators that are repeated across line breaks, like the $=$ below. I like the equation spacing in the ``Thimble projection reasoning for Airly-Lucas functions'' section; can we copy that here?]}
\begin{multline*}
     {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) \textcolor{magenta}{=} \\
     =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
\end{multline*}
hence 
%
\[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
%
Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:

\begin{align}
    K_{\mu}(z)& \label{eqn:K-mu}=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}-\mu, \frac{1}{2}+\mu;\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta\\
    &  \notag=-\frac{i}{2}\laplace_{\zeta,1} v_{\mu,1} . 
\end{align}
\subsubsection{The case $\mu=0$}
When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
\[ K_0(z) = \frac{1}{2\pi i} \int_ {\textcolor{orange}{\Omega}} \exp\left[z \cosh(t)\right]\,t\,dt. \]
\textcolor{orange}{Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$,} we can rewrite this formula as
\begin{align*}
K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
\end{align*}
with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}. Then equation \eqref{eqn:K-mu} gives

\begin{equation}\label{eqn:borel_bessel0}
    K_0(z)=\textcolor{red}{-}\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
\end{equation}
\begin{verify}
    We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning: from the expression of $K_0$ 
    \begin{equation}
        K_0(z)=\int_0^{\infty} \exp(-z\cosh(t)) dt
    \end{equation}
    we set $\zeta=\cosh(t)$, and choosing a branch for the square root
    \begin{align*}
        d\zeta & = \sinh(t) dt\\
        & =  \sqrt{\zeta^2-1} \, dt
    \end{align*}
    we finally get 
    \[\int_1^{\infty} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
\end{verify}

>>>>

Setting $u = \cosh(t/n)$ and recalling that
\begin{align*}
\cosh(n\tau) & = T_n(\cosh(\tau)) \\
\sinh(m\tau) & = U_{m-1}(\cosh(\tau)) \sinh(\tau),
\end{align*}
we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as
\begin{align}
\notag K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_\gamma \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt,
\end{align}
using the path $\mathcal{C}^\theta_j$ described below.
\begin{center}
\begin{tabular}{l|l|l}
When $j$ is\ldots & $\mathcal{C}^\theta_j$ comes from $-\infty$ along\ldots & and goes to $+\infty$ along\ldots \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} Odd & $(-\infty,0) + (j\pi-\theta)i$ & $(0, \infty) + (j\pi-\theta)i$ \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} Even & $(-\infty,0) + \big((j+1)\pi-\theta\big)i$ & $(0, \infty) + \big((j-1)\pi-\theta\big)i$ \\[1mm]
\end{tabular}
\end{center}
Because $\cosh(t)$ is periodic, $j$ only affects the integral through its parity.
\begin{figure}[ht]
    \centering
    \includegraphics[width=14cm]{figures/bessel-unrolled.png}
    \caption{The paths $\mathcal{C}_j$.}
    \label{fig:bessel_unrolled}
\end{figure}

For any $\mu \in \C \smallsetminus \Z$, the classical modified Bessel function $K_\mu(z)$ can be expressed as the thimble integral
\begin{equation}\label{int:mod-bessel-gen}
 K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\mathcal{C}^\theta_1} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt
\end{equation}
for $|\theta| < \tfrac{\pi}{2}$. This formula can be deduced, with a lot of finagling, from formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\begin{todo}{[Cite Watson too?]}\end{todo}.
\begin{verify}
\par
From equation~6.22(3) of Watson's \textit{A treatise on the theory of Bessel functions} (1944), p. 181 (the reference in \cite{dlmf}):
\begin{align*}
2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b}\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db.
\end{align*}
Hence,
\begin{align*}
4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big] \\
& = \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right]\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right]\,da \\
& \textcolor{OrangeRed}{= 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da} \\
& = 2\int_{-\infty}^0 e^{z\cosh(-\pi i+a)} \sinh\big(\mu(a-i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh\big(\mu(i\pi+a)\big)\,da
\end{align*}
\color{OrangeRed}
Stop at the highlighted line! This simplifies to the integral
\[ 2 \int_\gamma e^{z\cosh(t)} \sinh(\mu t)\,dt \]
along the contour $\gamma$ that runs rightward along $i\pi + \R$. \textcolor{magenta}{The integral on the next line is {\em not} the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, because it skips the segment along $i(-\pi, \pi)$.}
\par
\end{verify}
The integral converges when $z$ is in the right half-plane. Choosing a rational parameter $\mu = \tfrac{m}{n}$ gives formula~\eqref{integral:mod-bessel-lifted}, showing that $K^{(j)}_{m/n}(z)$ is the classical modified Bessel function $K_{m/n}(z)$ when $j$ is odd.

\color{RoyalBlue}
We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of the asymptotic of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
\color{black}
\textcolor{orange}{[\ldots]} We first recast the integral into the $\zeta$ plane by setting $-\zeta = \cosh(t)$
\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{\sinh(\mu t_+)}{\sinh(t_+)} - \frac{\sinh(\mu t_-)}{\sinh(t_-)} \right] d\zeta, \]
where $t_-$ and $t_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$. \textcolor{orange}{[\ldots]}
\color{RoyalBlue}
\begin{align*}
    K_\mu(z)& = -\frac{1}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\,\frac{\sinh(\mu t)}{\sinh(t)}\,d\zeta  & \\
    &=-\frac{\mu}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right)\,d\zeta & \cite[15.4.16]{dlmf}
\end{align*}
where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$. Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf} \textcolor{PaleVioletRed}{[Please clean up operators that are repeated across line breaks, like the $=$ below. I like the equation spacing in the ``Thimble projection reasoning for Airly-Lucas functions'' section; can we copy that here?]}
\begin{multline*}
     {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) \textcolor{magenta}{=} \\
     =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
\end{multline*}
hence 
%
\[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
%
Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:

\begin{align}
    K_{\mu}(z)& \label{eqn:K-mu}=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}-\mu, \frac{1}{2}+\mu;\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta\\
    &  \notag=-\frac{i}{2}\laplace_{\zeta,1} v_{\mu,1} . 
\end{align}
\subsubsection{The case $\mu=0$}
When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
\[ K_0(z) = \frac{1}{2\pi i} \int_ {\textcolor{orange}{\Omega}} \exp\left[z \cosh(t)\right]\,t\,dt. \]
\textcolor{orange}{Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$,} we can rewrite this formula as
\begin{align*}
K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
\end{align*}
with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}. Then equation \eqref{eqn:K-mu} gives
\color{black}
\begin{equation}\label{eqn:borel_bessel0}
    K_0(z)=\textcolor{red}{-}\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
\end{equation}
\begin{verify}
    We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning: from the expression of $K_0$ 
    \begin{equation}
        K_0(z)=\int_0^{\infty} \exp(-z\cosh(t)) dt
    \end{equation}
    we set $\zeta=\cosh(t)$, and choosing a branch for the square root
    \begin{align*}
        d\zeta & = \sinh(t) dt\\
        & =  \sqrt{\zeta^2-1} \, dt
    \end{align*}
    we finally get 
    \[\int_1^{\infty} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
\end{verify}
